Hydras \& Co.

### 2023-02-28 doc/chapter-fol.tex
First experiments on Fol notations

\inputsnippets{folExample2/ToyDef}

@@

Let us show a few examples (from ~\href{../theories/html/hydras.MoreAck.fol_Examples.html}{MoreAck.fol\_Examples}).

\inputsnippets{fol_Examples/arityTest}

@@

\inputsnippets{folExample2/toyNotation}

\inputsnippets{folExample2/smallTerms}

@@

\inputsnippets{fol_Examples/v1Plus0}

@@

For instance, the term $v_1+0$ is written as below.

\inputsnippets{fol_Examples/v1Plus0}

@@

\label{fol:examplesf1f2f3}
\begin{enumerate}
\item $\forall\,v_0, v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $\exists\,v_2,\, 0< v_2 \wedge 4=v_2+v_2$
\item $ v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $v_0= v_1 + v_1 \leftrightarrow v_0 = v_1 \times 2$
\end{enumerate}
\inputsnippets{fol_Examples/f1Example}

\begin{remark}[bound variables]
\inputsnippets{folExample2/boundVars}  
\end{remark}

@@

\inputsnippets{fol_Examples/FormulaRect}

@@

\inputsnippets{fol/depthDef,  fol_Examples/DepthCompute}

@@

\inputsnippets{fol_Examples/ltDepth1}

@@

\inputsnippets{fol_Examples/depthRecDemo}

@@

\inputsnippets{fol_Examples/depthRecDemo2}

@@

\inputsnippets{fol_Examples/freeVarExamples}

@@

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.FOL_notations.html}{MoreAck.FOL\_notations} and
~\href{../theories/html/hydras.MoreAck.LNN_notations.html}{MoreAck.LNN\_notations}.
Please note that these notation scopes are experimental: We are going to use them in examples and exercises before using them in large original proof scripts (in the \texttt{ordinals/Ackermann/} sub-directory).

@@

Prove the following lemma:
\inputsnippets{fol_Examples/eqRefl}

@@

Prove the following lemma:
\inputsnippets{fol_Examples/MPdiag}

@@

For instance, let us prove Peirce's rule.
 (in  ~\href{../theories/html/hydras.MoreAck.folPeirce.html}{MoreAck.folPeirce} ).

@@

\inputsnippets{folPeirce/prelude}

@@

\inputsnippets{folPeirce/PeirceProof}

@@

\inputsnippets{folPeirce/step1}

@@

\inputsnippets{folPeirce/step2}

@@

\inputsnippets{folPeirce/step3, folPeirce/step4}

>>>>

\inputsnippets{FolExamples/ToyDef}

@@

Let us show a few examples (from ~\href{../theories/html/hydras.MoreAck.FolExamples.html}{MoreAck.FolExamples}).

\inputsnippets{FolExamples/arityTest}

@@

\inputsnippets{FolExamples/toyNotation}

\inputsnippets{FolExamples/smallTerms}

@@

\inputsnippets{FolExamples/v1Plus0}

@@

@@

\label{fol:examplesf1f2f3}
\begin{enumerate}
\item $\forall\,v_0, v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $\exists\,v_2,\, 0< v_2 \wedge 4=v_2+v_2$
\item $ v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $v_0= v_1 + v_1 \leftrightarrow v_0 = v_1 \times 2$
\end{enumerate}
\inputsnippets{FolExamples/f1Example}

\begin{remark}[bound variables]
\inputsnippets{FolExamples/boundVars}  
\end{remark}

@@

\inputsnippets{FolExamples/FormulaRect}

@@

\inputsnippets{fol/depthDef,  FolExamples/DepthCompute}

@@

\inputsnippets{FolExamples/ltDepth1}

@@

\inputsnippets{FolExamples/depthRecDemo}

@@

\inputsnippets{FolExamples/depthRecDemo2}

@@

\inputsnippets{FolExamples/freeVarExamples}

@@

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.FOL_notations.html}{MoreAck.FOL\_notations} and
~\href{../theories/html/hydras.MoreAck.LNN.html}{MoreAck.LNN}.
Please note that these notation scopes are experimental: We are going to use them in examples and exercises before using them in large original proof scripts (in the \texttt{ordinals/Ackermann/} sub-directory).

@@

Prove the following lemma:
\inputsnippets{FolExamples/eqRefl}

@@

Prove the following lemma:
\inputsnippets{FolExamples/MPdiag}

@@

For instance, let us prove Peirce's rule.
 (in  ~\href{../theories/html/hydras.MoreAck.FolExamples.html}{MoreAck.FolExamples} ).

@@

%\inputsnippets{folPeirce/prelude}

@@

\inputsnippets{FolExamples/PeirceProof}

@@

\inputsnippets{FolExamples/step1}

@@

\inputsnippets{FolExamples/step2}

@@

\inputsnippets{FolExamples/step3, FolExamples/step4}
